What's in a Name? Linear Temporal Logic Literally Represents Time Lines

### 2023-01-02 paper/main.tex
bib

\begin{example}
    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $!p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $!p$, and so on. The lower timeline starts with one step of $!p$ and one step of $p$ outside the grey box, and then enter the infinite run of $!p$ and $p$ repeating.
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(p1)!0.5!(p2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};

>>>>

\begin{example}
    In \cref{fig:ex2}, one can reason about two parallel timelines: the upper timeline starts with $p$ at the first time step, followed by entering the grey box with one step of $\lnot p$ and one step of $p$. Then at the end of the grey box, we reenter the box, with the next time step being $\lnot p$, and so on. The lower timeline starts with one step of $\lnot p$ and one step of $p$ outside the grey box, and then enter the infinite run of $\lnot p$ and $p$ repeating.
    \begin{figure}[!h]
        \centering
        \begin{tikzpicture}
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p1) {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p2) [below=0.4cm of p1] {\!\!\!$p$\!\!\!};
        \node[draw, thick, fill=white, shape=ellipse, style={minimum width=1.5cm, minimum height=1cm}] (p3) [left= 1cm of p2] {\!\!\!$\lnot p$\!\!\!};
        \node (m) at ($(p1)!0.5!(p2)$) {};
        \node[shape=rectangle, fill=gray!30!white, style={minimum width=4.3cm, minimum height=1.25cm}] (g) [right= 1.35cm of m] {};
